---
title: "Lab3 _Q2_Practice to create a new Markdown Document"
author: "Sabrina Kakei Tse"
date: "September 21, 2018"
output: github_document
---

## This document lists out things I found interesting from 511 this week.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r What I learned from 511 this week}
# converting/coercing objects into different form in R

as.character(8.89)
as.numeric("8.89")

```

As a beginner to coding, I am more intrigued by R than by Python because of the ease of applying it. For example, if I have to square all the elements in a list, I have to set up a function to wrap a for-loop function in Python in order to do that:

### Step 1 in Python

```{python example}


def square(list):
  list=[]
  for x in list:
    list.apphend(x ** 2)
  
  return (list)


```
### Step 2 in Python
```{python recall the user-defined function}

a = [1,2,3,4,5]
square(a)

```

But all of these can be done in one step in R (MIND-BLOWN - that explained why Vincenzo walked away from the stage after he did the demo and said " Just that", as if he just "mic-dropped"" in our Thursday class):

```{r using r to create the same result}

a <- c(1,2,3,4,5)
a^2

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
